Click chemistry reveals an alternate mechanism for HPII catalase

### 2018-02-19 bb494/manuscript.tex
sd

>>>>

Substrate Flow, Loewen
There are H2O2 binding sites in the heme distal pocket and main channel
There are several input channels; what are their purposes?
There is a ``molecular ruler'' in the main channel which selects for H2O2 against water
Active site mutations which allow more water in slow down the rxn rate
This paper discusses unidirectional flow of H2O2 through the main channel

Active and inhibited catalase structures, tainer
This is the paper about the hydrophobic ``molecular ruler''
A hydrophobic region distal to the heme cleft contains phenylalanines, tryptophan and two valines
Authors propose that two waters (one h-bonded to human Asn148 and His75; other h-bonded to gln168 and asp128) form a ``ruler''
This ``ruler'' is far enough apart that only H2O2 can stably occupy the distance betweeen, thus allowing only H2O2 to enter, not H2O
This would explain why opening the perpendicular channel decreases the rate

Role of the lateral channel in catalase, loewen
This paper discusses the lateral channel as an exhaust channel
Proposes that perpendicular channel is the entrance, lateral channel is exit
